---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GroupBoosting

<!-- badges: start -->
<!-- badges: end -->

Group boosting is an algorithm developed to perform variable selection in a scalar-on-network regression setting, where the network has underlying group structure. 

## Installation

You can install the released version of GroupBoosting from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("EmilyLMorris/GroupBoosting")
```

## Example

Here is a very simple example to show how to use the method: 

```{r example}
library(GroupBoosting)

data1 = simul_dat_group(nodes = 6, n = 100, num.groups = 2, q.groups = 1, sparse_g = 0, dense_g = 1, effect_size = 5)
test1 = group_boosting_fit(data1$X, data1$Y, data1$group, total_steps=5000, step_size=1e-4, adj_var = 999, stop_tol=-1e-7, gamma = 0, lasso_lambda = 0.0314, weighted = FALSE)

cbind(test1$beta, data1$beta)

```

If you have other adjustment variables to account for in addition to the network this method, you can use the following example. 

```{r example2}

data2 = simul_dat_group(nodes = 6, n = 100, num.groups = 2, q.groups = 1, sparse_g = 0, dense_g = 1, effect_size = 5, adj_var = 3)
test2 = group_boosting_fit(data2$X, data2$Y, data2$group, total_steps=5000, step_size=1e-4, adj_var = c(1:3), stop_tol=-1e-7, gamma = 0, lasso_lambda = 0.0314, weighted = FALSE)

cbind(test2$beta, data2$beta[4:18])

```

